Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Added two refs to our PBML pubs
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1625 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit for parsing-based machine translation (written in Java). 
The first version implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

The toolkit has been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
support for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Josua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
\item
and a unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

We have introduced tools for visualizing two of the main data structures used
in Joshua \cite{PBML-2010-Josua-visualization}. Each visualization tool is implemented as a
stand-alone program that hooks into the pipeline, but they are distributed with
Joshua. The first program is a hypergraph visualizer. The user can choose from
a set of input sentences, then call the decoder to build the hypergraph.

>>>>

\textbf{Joshua} is an open-source toolkit for parsing-based machine translation (written in Java). 
The initial release of Joshua  \cite{joshua-wmt09} implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction} 
and minimum error rate training \cite{och-mert,Zaidan2009}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

The toolkit has been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
support for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Joshua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}, 
\item
and a unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

We have introduced tools for visualizing two of the main data structures used
in Joshua \cite{PBML-2010-Joshua-visualization}. Each visualization tool is implemented as a
stand-alone program that hooks into the pipeline, but they are distributed with
Joshua. The first program is a hypergraph visualizer. The user can choose from
a set of input sentences, then call the decoder to build the hypergraph.
